NoTitle

### 2017-05-21 SpringerLNCS/sections/Overview.tex
A little bit.

\section{A Running Example: \lstinline{DrawableDeck}}

@@

\subsection{More}
\begin{itemize}
	\item Code for the problem (Draw example)
	\item Potential fixes (delegation, renaming, traits, ....)
	\item How it is solved with our language (client code, simple explanation) + show update
\end{itemize}

@@

\paragraph{I. Delegation.}

\paragraph{II. Creating a \lstinline|draw()| method in \lstinline|DrawableDeck|, which explicitly overrides the old ones.}

\paragraph{III. Choosing one of them as the default method, like Mixins.}

\paragraph{IV. Method exclusion like traits.}

\paragraph{V. Method renaming.}
In previous solutions, only renaming can preserve the two different methods m(), 
but it’s cumbersome to do in practice: new names have to be introduced, and (probably) need to prefer one over another. 
Other solutions only preserve one method. Can we keep both methods without renaming?

\subsection{Solution in our language}
\begin{lstlisting}

\end{lstlisting}

>>>>

\section{A Running Example: DrawableDeck}

@@

@@

\paragraph{I. Delegation.} As an alternative to multiple inheritance, delegation can be used by
introducing two fields with \lstinline|Drawable| type and \lstinline|Deck| type, respectively. This avoids
method conflicts, nevertheless, delegation itself is too restricted in modularity, and meanwhile
introduces a lot of boilerplate.

\paragraph{II. Creating a \lstinline|draw()| method in \lstinline|DrawableDeck|, which explicitly overrides the old ones.}
This is a non-solution. It does not make any sense to override both methods with totally different functionalities, as old
methods have to be hidden.

\paragraph{III. Choosing one of them as the default method, like Mixins.} The mixin model can be applied to choose a
default one based on linearisation. Similarly, we want to preserve both features, rather than keeping only one of them.

\paragraph{IV. Method exclusion like traits.} Same reason as above.

\paragraph{V. Method renaming like traits.} This is probably what people do in most cases, by simply renaming one to avoid conflicts.
It can indeed preserve both features, however, it is cumbersome in practice, as introducing new names can affect other code blocks.
Certainly this is a workaround, not a solution.

\subsection{Solution in \MIM: \dispatchnamecaptical}
It uses dynamic dispatch.
